Reflections on reflection for \\ intuitionistic set theories

### 2024-08-11 paper-reflection.tex
to do

>>>>

Cite: https://link.springer.com/chapter/10.1007/BFb0061825

Cite: https://arxiv.org/pdf/1110.2430.pdf (page 10)

https://www.youtube.com/watch?v=lpOiuvzbBtw&list=PL6tK2CutTH9_lN7A0nFul_gEJUDSPJ91i&index=3
Timestamp 29:49
Aczel showed that RRS is stable under passage to sheaves on complete Heyting
algebras.
